---
title: "textcorpus"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  md_document:
    toc: true      
---

```{r, echo=FALSE}
desc <- suppressWarnings(readLines("DESCRIPTION"))
regex <- "(^Version:\\s+)(\\d+\\.\\d+\\.\\d+)"
loc <- grep(regex, desc)
ver <- gsub(regex, "\\2", desc[loc])
verbadge <- sprintf('<a href="https://img.shields.io/badge/Version-%s-orange.svg"><img src="https://img.shields.io/badge/Version-%s-orange.svg" alt="Version"/></a></p>', ver, ver)
````

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
knit_hooks$set(htmlcap = function(before, options, envir) {
  if(!before) {
    paste('<p class="caption"><b><em>',options$htmlcap,"</em></b></p>",sep="")
    }
    })
knitr::opts_knit$set(self.contained = TRUE, cache = FALSE)
knitr::opts_chunk$set(fig.path = "tools/figure/")
```

[![Build Status](https://travis-ci.org/trinker/textcorpus.svg?branch=master)](https://travis-ci.org/trinker/textcorpus)
[![Coverage Status](https://coveralls.io/repos/trinker/textcorpus/badge.svg?branch=master)](https://coveralls.io/r/trinker/textcorpus?branch=master)
`r verbadge`

**textcorpus** is collection of text courpus datasets.  The package also contains tools to enable easy community contributions to the package.  The underying premise is that the speech level data is stored with meta data as a list of two tibble data frames with a common key column.




# Installation

To download the development version of **textcorpus**:

Download the [zip ball](https://github.com/trinker/textcorpus/zipball/master) or [tar ball](https://github.com/trinker/textcorpus/tarball/master), decompress and run `R CMD INSTALL` on it, or use the **pacman** package to install the development version:

```r
if (!require("pacman")) install.packages("pacman")
pacman::p_load_gh("trinker/textcorpus")
```

# Data

```{r, echo=FALSE}
pacman::p_load(pander)
pander(description[-4], style = "grid", split.table = Inf, justify = c(rep('left', 4), 'right'))
```

# Demonstration

## Joining Corpus and Meta Data

**dplyr** akes joining the corpus and meta data easy.

```{r}
pacman::p_load(tidyverse, sentimentr, formality, readability)
pacman::p_load_current_gh('trinker/textcorpus')

nixon_tapes


dat <- nixon_tapes$corpus %>%
    dplyr::left_join(nixon_tapes$meta, by = 'id')

dat
```

## Text Scores

Here we calculate formality, sentiment, and readability measures.  An additional call to **dplyr**'s `left_jon` with a `Reduce` makes it easy to merge the various score frames into one frame.

```{r}
n_formality <- dat %>%
    filter(author == "Nixon") %>%
    with(formality(text, list(author, id, date)))

n_sentiment <- dat %>%
    filter(author == "Nixon") %>%
    with(sentiment_by(text, list(author, id, date)))

n_readability <- dat %>%
    filter(author == "Nixon") %>%
    with(readability(text, list(author, id, date)))

stats_dat <- list(n_formality, n_sentiment, n_readability) %>%
    Reduce(function(x, y) left_join(x, y, by=c("author", "id", "date")), .)
```

## Plotting the Text Scores Across Time

```{r}
stats_dat %>%
    select(date, F, ave_sentiment, Average_Grade_Level) %>%
    rename(Formality = F, Sentiment = ave_sentiment, Readbiltiy = Average_Grade_Level) %>%
    gather(Measure, Score, -date) %>%
    mutate(Date = as.factor(date), Date2 = as.numeric(Date)) %>%
    ggplot(aes(x = Date2, y = Score)) +
        geom_point() +
        geom_smooth(span = 0.4, fill = NA) +
        facet_wrap(~Measure, ncol = 1, scales = 'free_y') 

```

# Contact

You are welcome to:    
- submit suggestions and bug-reports at: <https://github.com/trinker/textcorpus/issues>    
- send a pull request on: <https://github.com/trinker/textcorpus/>    
- compose a friendly e-mail to: <tyler.rinker@gmail.com>    